A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-04-15 report_clean/proc.tex
bruno's changes
petites changements dans l'intro (General Issues: physics of the problem)+le fichier pour responce_reviewers
references

\begin{document}
\newcommand{\urev}[1]{{\color{red}#1}}
\newcommand{\mrev}[1]{{\color{blue}#1}}

@@

\begin{thebibliography}{99}
	\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
	Handbook of mathematical functions
	\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
\bibitem{cedar}
Charles, F., Despr\'es, B., Merhenberg, M, 
Enhanced convergence estimates for semi-lagrangian schemes Application to the Vlasov-Poisson equation, SIAM J. Numer. Anal. 2013, 51(2), 840-863.

@@

\bibitem{phdhattori}
T. Hattori, T. (2014).
D\'ecomposition de domaine pour la simulation Full-Wave dans un plasma froid.
Ph.D. Thesis, Universit\'e de
Lorraine.

@@

\bibitem{simon}
Simon Labrunie, Pierre Bertrand, Jean-Rodolphe Roche, Aurore Back,
Takashi Hattori, 
Electromagnetic wave propagation and absorption in
magnetised plasmas: variational formulations and
domain decomposition, Hal preprint 2014, https://hal.archives-ouvertes.fr/hal-01075137.

@@

\bibitem{Mouhot_2011} Mouhot, C., and Villani, C. (2011). On Landau damping. Acta mathematica, 207(1), 29-201.
\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
\bibitem{Xu_2006}Xu, L., ans Yuan, N. (2006). FDTD formulations for scattering from 3-D anisotropic magnetized plasma objects. Antennas and Wireless Propagation Letters, IEEE, 5(1), 335-338.
\end{thebibliography}

>>>>

\begin{document}
\newcommand{\urev}[1]{{\color{blue}#1}}
\newcommand{\arev}[1]{{\color{red}#1}}
\newcommand{\mrev}[1]{{\color{green}#1}}

@@

\begin{thebibliography}{99}
	\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
	Handbook of mathematical functions
	\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
\bibitem{cedar}
Charles, F., Despr\'es, B., Mehrenberg, M, 
Enhanced convergence estimates for semi-lagrangian schemes Application to the Vlasov-Poisson equation, SIAM J. Numer. Anal. 2013, 51(2), 840-863.

@@

\bibitem{phdhattori}
Hattori, T. (2014).
D\'ecomposition de domaine pour la simulation Full-Wave dans un plasma froid.
Ph.D. Thesis, Universit\'e de
Lorraine.

@@

\bibitem{simon}
Labrunie, S., Bertrand, P., Roche, J.-R., Back, A., and
Hattori, T. 
Electromagnetic wave propagation and absorption in
magnetised plasmas: variational formulations and
domain decomposition, Hal preprint 2014, https://hal.archives-ouvertes.fr/hal-01075137.

@@

\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
\bibitem{Xu_2006}Xu, L., and Yuan, N. (2006). FDTD formulations for scattering from 3-D anisotropic magnetized plasma objects. Antennas and Wireless Propagation Letters, IEEE, 5(1), 335-338.

\bibitem{singular_solutions}
Despr\'es, B., Imbert-G\'erard, L.-M. and Lafitte, O.. Singular solutions for the plasma at the resonance. 2014. <hal-01097364>

\end{thebibliography}
